---
title: "dags_R1"
author: "CEB"
date: '2025-03-20'
output: html_document
---

#check dag data consistency
#determine minimum adjustment sets for testing causal hypotheses

##load packages
```{r}
library(tidyverse) #for everything

#for dags:
library(dagitty)
library(ggdag)

#for corrplots:
library(corrplot)
library(rstatix)

```


###set plot theme
```{r}
theme_casey<-
  theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        text = element_text(size = 14, family = "Arial"),
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA)
        )

theme_set(theme_casey) 
  
```


#load data
```{r}

#For nutrient analysis:
seychelles_leaf_n15_dat<-read.csv("../data/seychelles_leaf_n15_dat.csv", stringsAsFactors = TRUE)  
seychelles_turf_n15_dat<-read.csv("../data/seychelles_turf_n15_dat.csv", stringsAsFactors = TRUE)  

seychelles_turf_n15_dat_2<-
  seychelles_turf_n15_dat%>%
  rename(turf_n15 = N15)


seychelles_leaf_n15_dat_2<-
  seychelles_leaf_n15_dat%>%
  rename(leaf_n15 = N15)

#For turf productivity analysis:
seychelles_turf_pp_by_cage_dat<-read.csv("../data/seychelles_turf_pp_by_cage_dat.csv", stringsAsFactors = TRUE)  

#For turf cover analysis, herbivore biomass, productivity analysis (all transect-level uvc data):
seychelles_uvc_dat<-read.csv("../data/seychelles_uvc_dat.csv", stringsAsFactors = TRUE)  

#for site-level data:
seychelles_all_site_level_dat<-read.csv("../data/seychelles_all_site_level_dat.csv", stringsAsFactors = TRUE)


```


#for testing dag data consistency overall, need to make column names match:
```{r}
dag_dat<-
  seychelles_all_site_level_dat%>%
   ungroup()%>%
  rename(exp = Exposure_J_m3,
         seabird = seabird.biomass.total,
          ln15 = mean_leaf_n15,
         tn15 = mean_turf_n15,
          pp = mean_turf_prod_mm_day,
         ht = mean_turf_height,
         sp = mean_herb_prod,
         bio_herb = mean_herb_bio,
         cover_turf = turf_cover,
         coral = coral_cover,
         pred = mean_pred_bio,
         struct = mean_structure)%>%
  dplyr::select(c(exp, seabird, ln15, tn15, pp, ht, sp, bio_herb, cover_turf, coral, pred, struct))
  

dag_dat
```

#DAG 1 - bottom-up effects - only uncontrolled for variables (i.e., exposure, predators, structure, coral cover):
```{r}

#copied from dagitty.net, with the position arguments removed (and unobserved variables explicitly named at end):

dag1_cexcl<-dagitty("
dag {
coral -> cover_turf
coral -> struct
cover_turf -> bio_herb
cover_turf -> sp
exp -> bio_herb
exp -> coral
exp -> cover_turf
exp -> ht
exp -> pp
exp -> pred
exp -> prior_herbivory
exp -> sp
exp -> struct
exp -> tn15
ht -> pp
pp -> bio_herb
pp -> sp
pred -> bio_herb
pred -> sp
prior_herbivory -> cover_turf
prior_herbivory -> ht
seabird -> ln15
seabird -> tn15
struct -> bio_herb
struct -> pred
struct -> sp
tn15 -> bio_herb
tn15 -> cover_turf
tn15 -> ht
tn15 -> pp
tn15 -> sp

prior_herbivory[unobserved]

}
")




```



#DAG 1 - bottom-up effects - all variables
```{r}
#"DAGs should include all measured and unmeasured variables required to depict the system or process under study, as well as all common causes of any pair of variables included in the DAG (Glymour & Greenland, 2008; Spirtes et al., 2001)." (Arif) - So don't need causes of one variable but not anything else*

#copied from dagitty.net, with the position arguments removed (and unobserved variables explicitly named at end):

dag1_all<-dagitty("dag {
coral -> cover_turf
coral -> struct
cover_turf -> bio_herb
cover_turf -> sp
depth -> bio_herb
depth -> coral
depth -> cover_turf
depth -> ht
depth -> pp
depth -> pred
depth -> prior_herbivory
depth -> sp
depth -> struct
depth -> tn15
exp -> bio_herb
exp -> coral
exp -> cover_turf
exp -> ht
exp -> pp
exp -> pred
exp -> prior_herbivory
exp -> sp
exp -> struct
exp -> tn15
fish -> bio_herb
fish -> pred
fish -> prior_herbivory
fish -> sp
ht -> pp
pp -> bio_herb
pp -> sp
pred -> bio_herb
pred -> sp
prior_herbivory -> cover_turf
prior_herbivory -> ht
seabird -> ln15
seabird -> tn15
struct -> bio_herb
struct -> pred
struct -> sp
tn15 -> bio_herb
tn15 -> cover_turf
tn15 -> ht
tn15 -> pp
tn15 -> sp
zone -> bio_herb
zone -> coral
zone -> cover_turf
zone -> ht
zone -> pp
zone -> pred
zone -> prior_herbivory
zone -> sp
zone -> struct
zone -> tn15


prior_herbivory[unobserved]
zone[adjusted]
depth[adjusted]
fish[adjusted]
}

")


```



#Alt DAG 2 - bottom-up + top-down effects - only uncontrolled for variables (i.e., exposure, predators, structure, coral cover):
```{r}
#copied from dagitty.net, with the position arguments removed (and unobserved variables explicitly named at end):

dag2_cexcl<-dagitty("dag {
bio_herb -> cover_turf
bio_herb -> herbivory
coral -> cover_turf
coral -> struct
exp -> bio_herb
exp -> coral
exp -> cover_turf
exp -> herbivory
exp -> ht
exp -> pp
exp -> pred
exp -> prior_turf
exp -> sp
exp -> struct
exp -> tn15
herbivory -> cover_turf
ht -> herbivory
ht -> pp
pp -> bio_herb
pp -> herbivory
pp -> sp
pred -> bio_herb
pred -> herbivory
pred -> sp
prior_turf -> cover_turf
prior_turf -> ht
seabird -> ln15
seabird -> tn15
sp -> cover_turf
sp -> herbivory
struct -> bio_herb
struct -> herbivory
struct -> pred
struct -> sp
tn15 -> bio_herb
tn15 -> cover_turf
tn15 -> herbivory
tn15 -> ht
tn15 -> pp
tn15 -> sp

herbivory[unobserved]
prior_turf[unobserved]
}
")

```


#Alt DAG 2 - bottom-up + top-down effects - all variables:
```{r}
#copied from dagitty.net, with the position arguments removed (and unobserved variables explicitly named at end):

dag2_all<-dagitty("dag {
bio_herb -> cover_turf
bio_herb -> herbivory
coral -> cover_turf
coral -> struct
depth -> bio_herb
depth -> coral
depth -> cover_turf
depth -> pp
depth -> pred
depth -> prior_turf
depth -> sp
depth -> tn15
exp -> bio_herb
exp -> coral
exp -> cover_turf
exp -> herbivory
exp -> ht
exp -> pp
exp -> pred
exp -> prior_turf
exp -> sp
exp -> struct
exp -> tn15
fish -> bio_herb
fish -> pred
fish -> sp
herbivory -> cover_turf
ht -> pp
pp -> bio_herb
pp -> herbivory
pp -> sp
pred -> bio_herb
pred -> herbivory
pred -> sp
prior_turf -> herbivory
prior_turf -> ht
seabird -> ln15
seabird -> tn15
sp -> cover_turf
sp -> herbivory
struct -> bio_herb
struct -> herbivory
struct -> pred
struct -> sp
tn15 -> bio_herb
tn15 -> cover_turf
tn15 -> herbivory
tn15 -> ht
tn15 -> pp
tn15 -> sp
zone -> bio_herb
zone -> cover_turf
zone -> ht
zone -> pp
zone -> pred
zone -> prior_turf
zone -> sp

herbivory[unobserved]
prior_turf[unobserved]
zone[adjusted]
depth[adjusted]
fish[adjusted]

}
")


```


#-----------test for dag data consitency:------

```{r}
#make reduced dag by removing variables with 0 variance (i.e., ones we controlled for):
#controls excluded dags (dag1_cexcl and dag2_cexcl) don't change. Other two dags just become the same as controls excluded. so use those to test for dag data consistency: 

#tests: dag 1 -----
dag_ss1 <- localTests(dag1_cexcl, data = dag_dat)
dag_ss1 
#looks pretty good - just leaf n15 not be independent. could add connection of leaf n15 with turf n15. likely connected by island size?

#calculate shipley's C:
C_stat <- -2 * sum(log(dag_ss1$p))
C_stat

#get degrees of freedom:
df <- nrow(dag_ss1)

#calculate p-value for C statistic:
p_value <- 1 - pchisq(C_stat, df)
cat("Shipley's C =", C_stat, "\nDegrees of freedom =", df, "\np-value =", p_value)
#very good dag data consistency (high p-value, so dag fits data well)


#tests: dag 2 -----
dag_ss2 <- localTests(dag2_cexcl, data = dag_dat)
dag_ss2 
#looks pretty good - just leaf n15 not be independent. could add connection of leaf n15 with turf n15. likely connected by island size?

#calculate shipley's C:
C_stat2 <- -2 * sum(log(dag_ss2$p))
C_stat2

#get degrees of freedom:
df2 <- nrow(dag_ss2)

#calculate p-value for C statistic:
p_value2 <- 1 - pchisq(C_stat2, df2)
cat("Shipley's C =", C_stat2, "\nDegrees of freedom =", df2, "\np-value =", p_value2)
#very good dag data consistency (high p-value, so dag fits data well)




```



#so based on above, try model with island size. first dag 1------
```{r}

dag1_cexcl_size<-dagitty("dag {
coral -> cover_turf
coral -> struct
cover_turf -> bio_herb
cover_turf -> sp
distance_to_seabirds -> ln15
distance_to_seabirds -> tn15
exp -> bio_herb
exp -> coral
exp -> cover_turf
exp -> ht
exp -> pp
exp -> pred
exp -> prior_herbivory
exp -> sp
exp -> struct
exp -> tn15
ht -> pp
island_size -> distance_to_seabirds
island_size -> ln15
island_size -> rats
island_size -> seabird
island_size -> tn15
pp -> bio_herb
pp -> sp
pred -> bio_herb
pred -> sp
prior_herbivory -> cover_turf
prior_herbivory -> ht
rats -> seabird
seabird -> ln15
seabird -> tn15
struct -> bio_herb
struct -> pred
struct -> sp
tn15 -> bio_herb
tn15 -> cover_turf
tn15 -> ht
tn15 -> pp
tn15 -> sp

prior_herbivory[unobserved]
distance_to_seabirds[unobserved]
}")


dag_dat2<-
  seychelles_all_site_level_dat%>%
   ungroup()%>%
   mutate(island_size = case_when(Island == "Aride"~71,
                                 Island == "Cousine"~26,
                                 Island == "Felicite"~268,
                                 Island == "Fregate"~206),
         rats_f = case_when(Island == "Aride"~"never_rats",
                                 Island == "Cousine"~"never_rats",
                                 Island == "Felicite"~"rats",
                                 Island == "Fregate"~"rats_eradicated"),
         rats = case_when(Island == "Aride"~0, #make an ordered factor for data checks
                                 Island == "Cousine"~0,
                                 Island == "Felicite"~2,
                                 Island == "Fregate"~1))%>%
  rename(exp = Exposure_J_m3,
         seabird = seabird.biomass.total,
          ln15 = mean_leaf_n15,
         tn15 = mean_turf_n15,
          pp = mean_turf_prod_mm_day,
         ht = mean_turf_height,
         sp = mean_herb_prod,
         bio_herb = mean_herb_bio,
         cover_turf = turf_cover,
         coral = coral_cover,
         pred = mean_pred_bio,
         struct = mean_structure)%>%
  dplyr::select(c(exp, seabird, ln15, tn15, pp, ht, sp, bio_herb, cover_turf, coral, pred, struct, rats, island_size))
  


#tests: dag 1 -----
dag_ss1_size <- localTests(dag1_cexcl_size, data = dag_dat2)
dag_ss1_size 
#now all good*

#calculate shipley's C:
C_stat <- -2 * sum(log(dag_ss1_size$p))
C_stat

#get degrees of freedom:
df <- nrow(dag_ss1_size)

#calculate p-value for C statistic:
p_value <- 1 - pchisq(C_stat, df)
cat("Shipley's C =", C_stat, "\nDegrees of freedom =", df, "\np-value =", p_value)
#very good dag data consistency (high p-value, so dag fits data well) - way higher p-value than previous model. use this one*



```


#so based on above, try model with island size. now dag 2------
```{r}

dag2_cexcl_size<-dagitty("dag {
bio_herb -> cover_turf
bio_herb -> herbivory
coral -> cover_turf
coral -> struct
distance_to_seabirds -> ln15
distance_to_seabirds -> tn15
exp -> bio_herb
exp -> coral
exp -> cover_turf
exp -> herbivory
exp -> ht
exp -> pp
exp -> pred
exp -> prior_turf
exp -> sp
exp -> struct
exp -> tn15
herbivory -> cover_turf
ht -> herbivory
ht -> pp
island_size -> distance_to_seabirds
island_size -> ln15
island_size -> rats
island_size -> seabird
island_size -> tn15
pp -> bio_herb
pp -> herbivory
pp -> sp
pred -> bio_herb
pred -> herbivory
pred -> sp
prior_turf -> cover_turf
prior_turf -> ht
rats -> seabird
seabird -> ln15
seabird -> tn15
sp -> cover_turf
sp -> herbivory
struct -> bio_herb
struct -> herbivory
struct -> pred
struct -> sp
tn15 -> bio_herb
tn15 -> cover_turf
tn15 -> herbivory
tn15 -> ht
tn15 -> pp
tn15 -> sp

herbivory[unobserved]
prior_turf[unobserved]
distance_to_seabirds[unobserved]

}")



#tests: dag 2 -----
dag_ss2_size <- localTests(dag2_cexcl_size, data = dag_dat2)
dag_ss2_size 
#now all good*

#calculate shipley's C:
C_stat <- -2 * sum(log(dag_ss2_size$p))
C_stat

#get degrees of freedom:
df <- nrow(dag_ss2_size)

#calculate p-value for C statistic:
p_value <- 1 - pchisq(C_stat, df)
cat("Shipley's C =", C_stat, "\nDegrees of freedom =", df, "\np-value =", p_value)
#very good dag data consistency (high p-value, so dag fits data well) - way higher p-value than previous model. use this one*



```


#also create models with island size for dags with all variables included (even those controlled for):
```{r}
###dag 1-----
dag1_all_size<-dagitty("dag {
coral -> cover_turf
coral -> struct
cover_turf -> bio_herb
cover_turf -> sp
depth -> bio_herb
depth -> coral
depth -> cover_turf
depth -> ht
depth -> pp
depth -> pred
depth -> prior_herbivory
depth -> sp
depth -> struct
depth -> tn15
distance_to_seabirds -> ln15
distance_to_seabirds -> tn15
exp -> bio_herb
exp -> coral
exp -> cover_turf
exp -> ht
exp -> pp
exp -> pred
exp -> prior_herbivory
exp -> sp
exp -> struct
exp -> tn15
fish -> bio_herb
fish -> pred
fish -> prior_herbivory
fish -> sp
ht -> pp
island_size -> distance_to_seabirds
island_size -> ln15
island_size -> rats
island_size -> seabird
island_size -> tn15
pp -> bio_herb
pp -> sp
pred -> bio_herb
pred -> sp
prior_herbivory -> cover_turf
prior_herbivory -> ht
rats -> seabird
seabird -> ln15
seabird -> tn15
struct -> bio_herb
struct -> pred
struct -> sp
tn15 -> bio_herb
tn15 -> cover_turf
tn15 -> ht
tn15 -> pp
tn15 -> sp
zone -> bio_herb
zone -> coral
zone -> cover_turf
zone -> ht
zone -> pp
zone -> pred
zone -> prior_herbivory
zone -> sp
zone -> struct
zone -> tn15

distance_to_seabirds[unobserved]
prior_herbivory[unobserved]
zone[adjusted]
depth[adjusted]
fish[adjusted]
}

")

###dag 2----------
dag2_all_size<-dagitty("dag {
bio_herb -> cover_turf
bio_herb -> herbivory
coral -> cover_turf
coral -> struct
depth -> bio_herb
depth -> coral
depth -> cover_turf
depth -> pp
depth -> pred
depth -> prior_turf
depth -> sp
depth -> tn15
distance_to_seabirds -> ln15
distance_to_seabirds -> tn15
exp -> bio_herb
exp -> coral
exp -> cover_turf
exp -> herbivory
exp -> ht
exp -> pp
exp -> pred
exp -> prior_turf
exp -> sp
exp -> struct
exp -> tn15
fish -> bio_herb
fish -> pred
fish -> sp
herbivory -> cover_turf
ht -> pp
island_size -> distance_to_seabirds
island_size -> ln15
island_size -> rats
island_size -> seabird
island_size -> tn15
pp -> bio_herb
pp -> herbivory
pp -> sp
pred -> bio_herb
pred -> herbivory
pred -> sp
prior_turf -> herbivory
prior_turf -> ht
rats -> seabird
seabird -> ln15
seabird -> tn15
sp -> cover_turf
sp -> herbivory
struct -> bio_herb
struct -> herbivory
struct -> pred
struct -> sp
tn15 -> bio_herb
tn15 -> cover_turf
tn15 -> herbivory
tn15 -> ht
tn15 -> pp
tn15 -> sp
zone -> bio_herb
zone -> cover_turf
zone -> ht
zone -> pp
zone -> pred
zone -> prior_turf
zone -> sp


distance_to_seabirds[unobserved]
herbivory[unobserved]
prior_turf[unobserved]
zone[adjusted]
depth[adjusted]
fish[adjusted]

}
")

```



###-----minimum adjustment sets-------####
#need for: dag1_cexcl, dag2_cexcl, dag1_all, dag2_all, dag1_cexl_size, dag2_cexl_size dag1_all_size, dag2_all_size

#dag1_cexcl
```{r}

##h1-h2
adjustmentSets(dag1_cexcl, exposure = "seabird", outcome = "ln15",
               type = "minimal", effect = c("total", "direct"))
#none needed


adjustmentSets(dag1_cexcl, exposure = "seabird", outcome = "tn15",
               type = "minimal", effect = c("total" ))
#none needed

adjustmentSets(dag1_cexcl, exposure = "seabird", outcome = "tn15",
               type = "minimal", effect = c( "direct"))
#none needed


##h3-h4
adjustmentSets(dag1_cexcl, exposure = "tn15", outcome = "pp",
               type = "minimal", effect = c("total"))
#{ exp }


adjustmentSets(dag1_cexcl, exposure = "tn15", outcome = "pp",
               type = "minimal", effect = c("direct"))
#{ exp, ht }


adjustmentSets(dag1_cexcl, exposure = "tn15", outcome = "cover_turf",
               type = "minimal", effect = c("total"))
#{ exp }


adjustmentSets(dag1_cexcl, exposure = "tn15", outcome = "cover_turf",
               type = "minimal", effect = c("direct"))
#{ exp }


##h5-h6
adjustmentSets(dag1_cexcl, exposure = "pp", outcome = "sp",
               type = "minimal", effect = c("total"))
#{ cover_turf, exp, struct, tn15 }
#{ coral, cover_turf, exp, tn15 }
#{ exp, ht, tn15 }

adjustmentSets(dag1_cexcl, exposure = "pp", outcome = "sp",
               type = "minimal", effect = c("direct"))
#{ cover_turf, exp, struct, tn15 }
#{ coral, cover_turf, exp, tn15 }
#{ exp, ht, tn15 }

adjustmentSets(dag1_cexcl, exposure = "pp", outcome = "bio_herb",
               type = "minimal", effect = c("total"))
#{ cover_turf, exp, struct, tn15 }
#{ coral, cover_turf, exp, tn15 }
#{ exp, ht, tn15 }

adjustmentSets(dag1_cexcl, exposure = "pp", outcome = "bio_herb",
               type = "minimal", effect = c("direct"))
#{ cover_turf, exp, struct, tn15 }
#{ coral, cover_turf, exp, tn15 }
#{ exp, ht, tn15 }


##h7-h8
adjustmentSets(dag1_cexcl, exposure = "cover_turf", outcome = "sp",
               type = "minimal", effect = c("total"))
#{ exp, pp, struct, tn15 }
#{ coral, exp, pp, tn15 }
#{ exp, ht, struct, tn15 }
#{ coral, exp, ht, tn15 }

adjustmentSets(dag1_cexcl, exposure = "cover_turf", outcome = "sp",
               type = "minimal", effect = c("direct"))
#{ exp, pp, struct, tn15 }
#{ coral, exp, pp, tn15 }
#{ exp, ht, struct, tn15 }
#{ coral, exp, ht, tn15 }


adjustmentSets(dag1_cexcl, exposure = "cover_turf", outcome = "bio_herb",
               type = "minimal", effect = c("total"))
#{ exp, pp, struct, tn15 }
#{ coral, exp, pp, tn15 }
#{ exp, ht, struct, tn15 }
#{ coral, exp, ht, tn15 }

adjustmentSets(dag1_cexcl, exposure = "cover_turf", outcome = "bio_herb",
               type = "minimal", effect = c("direct"))
#{ exp, pp, struct, tn15 }
#{ coral, exp, pp, tn15 }
#{ exp, ht, struct, tn15 }
#{ coral, exp, ht, tn15 }


##h9-h10
adjustmentSets(dag1_cexcl, exposure = "tn15", outcome = "sp",
               type = "minimal", effect = c( "direct"))
#{ cover_turf, exp, pp, struct }
#{ coral, cover_turf, exp, pp }

adjustmentSets(dag1_cexcl, exposure = "tn15", outcome = "sp",
               type = "minimal", effect = c( "total"))
#{ exp }


adjustmentSets(dag1_cexcl, exposure = "tn15", outcome = "bio_herb",
               type = "minimal", effect = c( "direct"))
#{ cover_turf, exp, pp, struct }
#{ coral, cover_turf, exp, pp }


adjustmentSets(dag1_cexcl, exposure = "tn15", outcome = "bio_herb",
               type = "minimal", effect = c( "total"))
#{ exp }



#notes: sp and bio_herb always have same adjustment sets, so can just use one to test in future models

```


#dag1_cexcl_size
```{r}

##h1-h2
adjustmentSets(dag1_cexcl_size, exposure = "seabird", outcome = "ln15",
               type = "minimal", effect = c("total", "direct"))
#none needed --> now need { island_size } for all of these


adjustmentSets(dag1_cexcl_size, exposure = "seabird", outcome = "tn15",
               type = "minimal", effect = c("total" ))
#none needed --> now need { island_size } for all of these

adjustmentSets(dag1_cexcl_size, exposure = "seabird", outcome = "tn15",
               type = "minimal", effect = c( "direct"))
#none needed --> now need { island_size } for all of these


##h3-h4
adjustmentSets(dag1_cexcl_size, exposure = "tn15", outcome = "pp",
               type = "minimal", effect = c("total"))
#{ exp }


adjustmentSets(dag1_cexcl_size, exposure = "tn15", outcome = "pp",
               type = "minimal", effect = c("direct"))
#{ exp, ht }


adjustmentSets(dag1_cexcl_size, exposure = "tn15", outcome = "cover_turf",
               type = "minimal", effect = c("total"))
#{ exp }


adjustmentSets(dag1_cexcl_size, exposure = "tn15", outcome = "cover_turf",
               type = "minimal", effect = c("direct"))
#{ exp }


##h5-h6
adjustmentSets(dag1_cexcl_size, exposure = "pp", outcome = "sp",
               type = "minimal", effect = c("total"))
#{ cover_turf, exp, struct, tn15 }
#{ coral, cover_turf, exp, tn15 }
#{ exp, ht, tn15 }

adjustmentSets(dag1_cexcl_size, exposure = "pp", outcome = "sp",
               type = "minimal", effect = c("direct"))
#{ cover_turf, exp, struct, tn15 }
#{ coral, cover_turf, exp, tn15 }
#{ exp, ht, tn15 }



##h7-h8
adjustmentSets(dag1_cexcl_size, exposure = "cover_turf", outcome = "sp",
               type = "minimal", effect = c("total"))
#{ exp, pp, struct, tn15 }
#{ coral, exp, pp, tn15 }
#{ exp, ht, struct, tn15 }
#{ coral, exp, ht, tn15 }

adjustmentSets(dag1_cexcl_size, exposure = "cover_turf", outcome = "sp",
               type = "minimal", effect = c("direct"))
#{ exp, pp, struct, tn15 }
#{ coral, exp, pp, tn15 }
#{ exp, ht, struct, tn15 }
#{ coral, exp, ht, tn15 }



##h9-h10
adjustmentSets(dag1_cexcl_size, exposure = "tn15", outcome = "sp",
               type = "minimal", effect = c( "direct"))
#{ cover_turf, exp, pp, struct }
#{ coral, cover_turf, exp, pp }

adjustmentSets(dag1_cexcl_size, exposure = "tn15", outcome = "sp",
               type = "minimal", effect = c( "total"))
#{ exp }



#note - adding island size and rats ONLY affects turf and leaf n15 as response models. All else is identical****

```

#dag1_all_size
```{r}

##h1-h2
adjustmentSets(dag1_all_size, exposure = "seabird", outcome = "ln15",
               type = "minimal", effect = c("total"))
#{ depth, fish, island_size, zone } -> so in model still just need island_size. all else adjusted for. 

adjustmentSets(dag1_all_size, exposure = "seabird", outcome = "ln15",
               type = "minimal", effect = c("direct"))
#{ depth, fish, island_size, zone } -> so in model still just need island_size. all else adjusted for. 


adjustmentSets(dag1_all_size, exposure = "seabird", outcome = "tn15",
               type = "minimal", effect = c("total" ))
#{ depth, fish, island_size, zone } -> so in model still just need island_size. all else adjusted for. 

adjustmentSets(dag1_all_size, exposure = "seabird", outcome = "tn15",
               type = "minimal", effect = c( "direct"))
#{ depth, fish, island_size, zone } -> so in model still just need island_size. all else adjusted for. 


##h3-h4
adjustmentSets(dag1_all_size, exposure = "tn15", outcome = "pp",
               type = "minimal", effect = c("total"))
#{ depth, exp, fish, zone } -> so still just need exposure


adjustmentSets(dag1_all_size, exposure = "tn15", outcome = "pp",
               type = "minimal", effect = c("direct"))
#{ depth, exp, fish, ht, zone } -> so still need exp and ht


adjustmentSets(dag1_all_size, exposure = "tn15", outcome = "cover_turf",
               type = "minimal", effect = c("total"))
#{ depth, exp, fish, zone } -> so still just need exposure


adjustmentSets(dag1_all_size, exposure = "tn15", outcome = "cover_turf",
               type = "minimal", effect = c("direct"))
#{ depth, exp, fish, ht, zone }  -> so still just need exposure


##h5-h6
adjustmentSets(dag1_all_size, exposure = "pp", outcome = "sp",
               type = "minimal", effect = c("total"))
#{ cover_turf, depth, exp, fish, struct, tn15, zone } --> same as before = { cover_turf, exp, struct, tn15 }
#{ coral, cover_turf, depth, exp, fish, tn15, zone } --> same as before = { coral, cover_turf, exp, tn15 }
#{ depth, exp, fish, ht, tn15, zone } --> same as before = { exp, ht, tn15 }


adjustmentSets(dag1_all_size, exposure = "pp", outcome = "sp",
               type = "minimal", effect = c("direct"))
#{ cover_turf, depth, exp, fish, struct, tn15, zone } --> same as before = { cover_turf, exp, struct, tn15 }
#{ coral, cover_turf, depth, exp, fish, tn15, zone } --> same as before = { coral, cover_turf, exp, tn15 }
#{ depth, exp, fish, ht, tn15, zone } --> same as before = { exp, ht, tn15 }


##h7-h8
adjustmentSets(dag1_all_size, exposure = "cover_turf", outcome = "sp",
               type = "minimal", effect = c("total"))
#{ depth, exp, fish, pp, struct, tn15, zone } --> same as before = { exp, pp, struct, tn15 }
#{ coral, depth, exp, fish, pp, tn15, zone } --> same as before = { coral, exp, pp, tn15 }
#{ depth, exp, fish, ht, struct, tn15, zone }  --> same as before = { exp, ht, struct, tn15 }
#{ coral, depth, exp, fish, ht, tn15, zone } --> same as before =  { coral, exp, ht, tn15 }



adjustmentSets(dag1_all_size, exposure = "cover_turf", outcome = "sp",
               type = "minimal", effect = c("direct"))
#{ depth, exp, fish, pp, struct, tn15, zone } --> same as before = { exp, pp, struct, tn15 }
#{ coral, depth, exp, fish, pp, tn15, zone } --> same as before = { coral, exp, pp, tn15 }
#{ depth, exp, fish, ht, struct, tn15, zone }  --> same as before = { exp, ht, struct, tn15 }
#{ coral, depth, exp, fish, ht, tn15, zone } --> same as before =  { coral, exp, ht, tn15 }



##h9-h10
adjustmentSets(dag1_all_size, exposure = "tn15", outcome = "sp",
               type = "minimal", effect = c( "direct"))
#{ cover_turf, depth, exp, fish, pp, struct, zone } --> same as before = { cover_turf, exp, pp, struct }
#{ coral, cover_turf, depth, exp, fish, pp, zone } --> same as before = { coral, cover_turf, exp, pp }


adjustmentSets(dag1_all_size, exposure = "tn15", outcome = "sp",
               type = "minimal", effect = c( "total"))
#{ depth, exp, fish, zone } -- same as before = { exp }



#note - all identical to model without all these extra variables when make the models***

```



#dag2_cexcl_size
```{r}

##h1-h2
adjustmentSets(dag2_cexcl_size, exposure = "seabird", outcome = "ln15",
               type = "minimal", effect = c("total"))

adjustmentSets(dag2_cexcl_size, exposure = "seabird", outcome = "ln15",
               type = "minimal", effect = c("direct"))

adjustmentSets(dag2_cexcl_size, exposure = "seabird", outcome = "tn15",
               type = "minimal", effect = c("total" ))

adjustmentSets(dag2_cexcl_size, exposure = "seabird", outcome = "tn15",
               type = "minimal", effect = c( "direct"))

#same, still need { island_size } for all of these


##h3-h4
adjustmentSets(dag2_cexcl_size, exposure = "tn15", outcome = "pp",
               type = "minimal", effect = c("total"))
#same: { exp }


adjustmentSets(dag2_cexcl_size, exposure = "tn15", outcome = "pp",
               type = "minimal", effect = c("direct"))
#same: { exp, ht }


adjustmentSets(dag2_cexcl_size, exposure = "tn15", outcome = "cover_turf",
               type = "minimal", effect = c("total"))
#same: { exp }


adjustmentSets(dag2_cexcl_size, exposure = "tn15", outcome = "cover_turf",
               type = "minimal", effect = c("direct"))
#NOW NOT POSSIBLE*****


##h5-h6
adjustmentSets(dag2_cexcl_size, exposure = "pp", outcome = "sp",
               type = "minimal", effect = c("total"))
#NOW JUST: { exp, tn15 } *****

adjustmentSets(dag2_cexcl_size, exposure = "pp", outcome = "sp",
               type = "minimal", effect = c("direct"))
#NOW JUST: { exp, tn15 } *****



##h7-h8 - REVERSE
adjustmentSets(dag2_cexcl_size, exposure = "sp", outcome = "cover_turf",
               type = "minimal", effect = c("total"))
#{ exp, pp, pred, struct, tn15 } ***** obviously different b/c different response/predictor

adjustmentSets(dag2_cexcl_size, exposure = "sp", outcome = "cover_turf",
               type = "minimal", effect = c("direct"))
#NOT POSSIBLE - BECAUSE HERBIVORY IS SEPERATE***


##h9-h10
adjustmentSets(dag2_cexcl_size, exposure = "tn15", outcome = "sp",
               type = "minimal", effect = c( "direct"))
#NOW JUST: { exp, pp } ******** but don't really care about this - from above not much direct effect. could still double-check it's consistent I guess. 

adjustmentSets(dag2_cexcl_size, exposure = "tn15", outcome = "sp",
               type = "minimal", effect = c( "total"))
#same: { exp }


```


#dag2_all_size
```{r}

##h1-h2
adjustmentSets(dag2_all_size, exposure = "seabird", outcome = "ln15",
               type = "minimal", effect = c("total"))

adjustmentSets(dag2_all_size, exposure = "seabird", outcome = "ln15",
               type = "minimal", effect = c("direct"))

adjustmentSets(dag2_all_size, exposure = "seabird", outcome = "tn15",
               type = "minimal", effect = c("total" ))

adjustmentSets(dag2_all_size, exposure = "seabird", outcome = "tn15",
               type = "minimal", effect = c( "direct"))

#same, still need { depth, fish, island_size, zone }, which reduces to island_size for all of these


##h3-h4
adjustmentSets(dag2_all_size, exposure = "tn15", outcome = "pp",
               type = "minimal", effect = c("total"))
#same: { depth, exp, fish, zone } which reduces to { exp }


adjustmentSets(dag2_all_size, exposure = "tn15", outcome = "pp",
               type = "minimal", effect = c("direct"))
#same: { depth, exp, fish, ht, zone } which reduces to { exp, ht }


adjustmentSets(dag2_all_size, exposure = "tn15", outcome = "cover_turf",
               type = "minimal", effect = c("total"))
#same: { depth, exp, fish, zone } which reduces to { exp }


adjustmentSets(dag2_all_size, exposure = "tn15", outcome = "cover_turf",
               type = "minimal", effect = c("direct"))
#NOW NOT POSSIBLE (same as model with controls excluded)*****


##h5-h6
adjustmentSets(dag2_all_size, exposure = "pp", outcome = "sp",
               type = "minimal", effect = c("total"))
#NOW JUST: { depth, exp, fish, tn15, zone } which reduces to { exp, tn15 } *****
#so same as model with controls excluded

adjustmentSets(dag2_all_size, exposure = "pp", outcome = "sp",
               type = "minimal", effect = c("direct"))
#NOW JUST: { depth, exp, fish, tn15, zone } which reduces to { exp, tn15 } *****
#so same as model with controls excluded




##h7-h8 - REVERSE
adjustmentSets(dag2_all_size, exposure = "sp", outcome = "cover_turf",
               type = "minimal", effect = c("total"))
#{ depth, exp, fish, pp, pred, struct, tn15, zone }, which reduces to { exp, pp, pred, struct, tn15 } 
#***** obviously different than dag1 b/c different response/predictor, but reduces to same as dag2 model with controls excluded

adjustmentSets(dag2_all_size, exposure = "sp", outcome = "cover_turf",
               type = "minimal", effect = c("direct"))
#NOT POSSIBLE - BECAUSE HERBIVORY IS SEPERATE***


##h9-h10
adjustmentSets(dag2_all_size, exposure = "tn15", outcome = "sp",
               type = "minimal", effect = c( "direct"))
#NOW JUST: { depth, exp, fish, pp, zone } which reduces to { exp, pp } ******** 
#***** different than dag1, but reduces to same as dag2 model with controls excluded

adjustmentSets(dag2_all_size, exposure = "tn15", outcome = "sp",
               type = "minimal", effect = c( "total"))
#{ depth, exp, fish, zone }, which reduces to { exp }. same same. 


```


##correlation plots:
```{r}
library(corrplot)
library(rstatix)

corr_dat<-
  seychelles_all_site_level_dat%>%
  select(mean_turf_n15, mean_turf_prod_mm_day, turf_cover, mean_herb_prod, mean_herb_bio)%>%
    rename("turf nutrients" = mean_turf_n15,
         "turf productivity" = mean_turf_prod_mm_day,
         "turf cover" = turf_cover,
         "herbivore productivity" = mean_herb_prod,
         "herbivore biomass" = mean_herb_bio)


corr_dat_log<-
  seychelles_all_site_level_dat%>%
  mutate(log_herb_bio = log(mean_herb_bio),
         log_herb_prod = log(mean_herb_prod),
         log_turf_cover = log(turf_cover))%>%
  select(mean_turf_n15, mean_turf_prod_mm_day, log_turf_cover, log_herb_prod, log_herb_bio)%>%
  rename("turf nutrients" = mean_turf_n15,
         "turf productivity" = mean_turf_prod_mm_day,
         "turf cover" = log_turf_cover,
         "herbivore productivity" = log_herb_prod,
         "herbivore biomass" = log_herb_bio)


##corr plots
#non-logged:----
corrplot(cor(corr_dat), type = "upper")
         #,addCoef.col = "gray", addCoefasPercent = FALSE)

#logged
corrplot(cor(corr_dat_log), type = "upper")
         #,addCoef.col = "gray", addCoefasPercent = FALSE)


#pdf(file = "../outputs/figures/corr_plot_log.pdf")
corrplot(cor(corr_dat_log),
     type="upper",
     pch.cex = 0.8,
     pch.col = "red",
     tl.col="black",
     tl.cex=1,
     outline=TRUE)
#dev.off()




#pdf(file = "../outputs/figures/corr_plot_notlog.pdf")
corrplot(cor(corr_dat),
     type="upper",
     pch.cex = 0.8,
     pch.col = "red",
     tl.col="black",
     tl.cex=1,
     outline=TRUE)
#dev.off()

```


```

