---
title: "herbivore-feeding-group-analysis"
author: "CEB"
date: '2024-09-25'
output: html_document
---

#load packages
```{r}
library(tidyverse)

#for bayesian analysis:
library(brms)
library(tidybayes)

#for plotting:
library(cowplot)

library(jtools)

```


###set plot theme
```{r}
theme_casey<-
  theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), 
        text = element_text(size = 14, family = "Arial"),
        rect = element_rect(fill = "transparent"),  
        plot.background = element_rect(fill = "transparent", color = NA)
        )

theme_set(theme_casey) 
  
```


#load  data and combine
```{r}
#turf cover and nutrient data----
turf_cover_iso_dat<-read.csv("../data/seychelles_turf_cover_isotopes_by_transect.csv")

#turf growth data---
turf_growth_iso_dat<-read.csv("../data/seychelles_turf_pp_iso_by_cage.csv")
#aggregate by site:
turf_growth_iso_site_dat<-
  turf_growth_iso_dat%>%
    group_by(Island, Site)%>%
  summarize(mean_turf_prod_mm_day = mean(Turf_growth_mm_per_day, na.rm = TRUE),
            se_turf_prod_mm_day = sd(Turf_growth_mm_per_day, na.rm = TRUE)/sqrt(length(Turf_growth_mm_per_day)))
turf_growth_iso_site_dat

#herbivore info (from productivity calculations file)----
herbivore_fg_dat<-read.csv("../data/seychelles_herbivore_biomass_productivity_by_transect_and_feeding_group.csv")

#combine---
str(turf_cover_iso_dat)
str(herbivore_fg_dat)

#first turf cover with turf growth (nutrients should match)
turf_all_dat<-left_join(turf_cover_iso_dat, turf_growth_iso_site_dat, 
                                    by =c("Island", "Site"))
turf_all_dat

herbivore_fg_turf_dat<-left_join(herbivore_fg_dat, turf_all_dat,
                                    by =c("Island", "Site", "Transect"))
herbivore_fg_turf_dat

```


#seperate by feeding group
```{r}
#now seperate data per group:----
browser_dat<-
  herbivore_fg_turf_dat%>%
  filter(FG.fine == "Browser")

brusher_dat<-
  herbivore_fg_turf_dat%>%
  filter(FG.fine == "Brusher")

cropper_dat<-
  herbivore_fg_turf_dat%>%
  filter(FG.fine == "Cropper")

excavator_dat<-
  herbivore_fg_turf_dat%>%
  filter(FG.fine == "Excavator")

farmer_dat<-
  herbivore_fg_turf_dat%>%
  filter(FG.fine == "Farmer")

scraper_dat<-
  herbivore_fg_turf_dat%>%
  filter(FG.fine == "Scraper")

#add column for centered, log data:----
browser_dat_c<-
  browser_dat%>%
  mutate(turf_n15_c = base::scale(mean_turf_n15, center = TRUE, scale = FALSE),
         turf_prop_c = base::scale(turf_prop, center = TRUE, scale = FALSE),
         turf_productivity_c = base::scale(mean_turf_prod_mm_day, center = TRUE, scale = FALSE),
         log_herb_bio = log(biomass_kg_ha+1),
         log_herb_prod = log(productivity_kg_ha_day+1))
browser_dat_c

brusher_dat_c<-
  brusher_dat%>%
  mutate(turf_n15_c = base::scale(mean_turf_n15, center = TRUE, scale = FALSE),
         turf_prop_c = base::scale(turf_prop, center = TRUE, scale = FALSE),
         turf_productivity_c = base::scale(mean_turf_prod_mm_day, center = TRUE, scale = FALSE),
         log_herb_bio = log(biomass_kg_ha+1),
         log_herb_prod = log(productivity_kg_ha_day+1))
brusher_dat_c

cropper_dat_c<-
  cropper_dat%>%
  mutate(turf_n15_c = base::scale(mean_turf_n15, center = TRUE, scale = FALSE),
         turf_prop_c = base::scale(turf_prop, center = TRUE, scale = FALSE),
         turf_productivity_c = base::scale(mean_turf_prod_mm_day, center = TRUE, scale = FALSE),
         log_herb_bio = log(biomass_kg_ha+1),
         log_herb_prod = log(productivity_kg_ha_day+1))
cropper_dat_c

excavator_dat_c<-
  excavator_dat%>%
  mutate(turf_n15_c = base::scale(mean_turf_n15, center = TRUE, scale = FALSE),
         turf_prop_c = base::scale(turf_prop, center = TRUE, scale = FALSE),
         turf_productivity_c = base::scale(mean_turf_prod_mm_day, center = TRUE, scale = FALSE),
         log_herb_bio = log(biomass_kg_ha+1),
         log_herb_prod = log(productivity_kg_ha_day+1))
excavator_dat_c

farmer_dat_c<-
  farmer_dat%>%
  mutate(turf_n15_c = base::scale(mean_turf_n15, center = TRUE, scale = FALSE),
         turf_prop_c = base::scale(turf_prop, center = TRUE, scale = FALSE),
         turf_productivity_c = base::scale(mean_turf_prod_mm_day, center = TRUE, scale = FALSE),
         log_herb_bio = log(biomass_kg_ha+1),
         log_herb_prod = log(productivity_kg_ha_day+1))
farmer_dat_c

scraper_dat_c<-
  scraper_dat%>%
  mutate(turf_n15_c = base::scale(mean_turf_n15, center = TRUE, scale = FALSE),
         turf_prop_c = base::scale(turf_prop, center = TRUE, scale = FALSE),
         turf_productivity_c = base::scale(mean_turf_prod_mm_day, center = TRUE, scale = FALSE),
         log_herb_bio = log(biomass_kg_ha+1),
         log_herb_prod = log(productivity_kg_ha_day+1))
scraper_dat_c

```


####Bayesian analysis based on DAGs - effect of turf productivity on herbivore productivity, by feeding group----
```{r}

##browser---
browser_prod_log_mod<-
  brm(log_herb_prod ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = browser_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/browser_prod_log_mod") #5 divergent trans
print(browser_prod_log_mod)
pp_check(browser_prod_log_mod) #not sampling peak**


hypothesis(browser_prod_log_mod, "turf_productivity_c>0")
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	    0.38	    4.04	      -2.31	     3.3	      2.16                    	0.68	



##brusher---
brusher_prod_log_mod<-
  brm(log_herb_prod ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = brusher_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/brusher_prod_log_mod") #18 divergent trans
print(brusher_prod_log_mod) 
plot(brusher_prod_log_mod)
pp_check(brusher_prod_log_mod) #looks pretty good


hypothesis(brusher_prod_log_mod, "turf_productivity_c>0") 
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	     0.3	      2.63    	-0.88	    1.33	      2.45	                0.71		




##cropper---
cropper_prod_log_mod<-
  brm(log_herb_prod ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = cropper_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/cropper_prod_log_mod") #4 divergent trans
print(cropper_prod_log_mod) 
plot(cropper_prod_log_mod)
pp_check(cropper_prod_log_mod) #not quite sampling peak


hypothesis(cropper_prod_log_mod, "turf_productivity_c>0") 
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	      1.03    	4.52	  -4.14   	5.75        	3.65	                      0.78	


##excavator---
excavator_prod_log_mod<-
  brm(log_herb_prod ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = excavator_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/excavator_prod_log_mod") #29 divergent trans
print(excavator_prod_log_mod)
plot(excavator_prod_log_mod)
pp_check(excavator_prod_log_mod) #looks good


hypothesis(excavator_prod_log_mod, "turf_productivity_c>0") 
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	     -0.6	    2.48      	-3.57	    1.95        	0.25	                0.2		



##farmer---
farmer_prod_log_mod<-
  brm(log_herb_prod ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = farmer_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/farmer_prod_log_mod") #9 divergent trans
print(farmer_prod_log_mod) 
plot(farmer_prod_log_mod)
pp_check(farmer_prod_log_mod) #looks good


hypothesis(farmer_prod_log_mod, "turf_productivity_c>0") 
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	   -0.27    	0.95    	-1.32	    0.63        	0.27                    	0.22	



##scraper---
scraper_prod_log_mod<-
  brm(log_herb_prod ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = scraper_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/scraper_prod_log_mod") # 8 divergent trans
print(scraper_prod_log_mod) 
plot(scraper_prod_log_mod)
pp_check(scraper_prod_log_mod) #looks good


hypothesis(scraper_prod_log_mod, "turf_productivity_c>0") 
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	    	0.22	    3.65  	-3.66	    4.27	        1.7	                          0.63	


#some divergent transition issues, but not many other distributions to try that have helped. Secondary analysis, proceed with this for now. 
#compare to non-log models to see if any improvement, and if any conclusions change:-----

##browser---
browser_prod_mod<-
  brm(productivity_kg_ha_day ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = browser_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/browser_prod_mod") #9 divergent trans
print(browser_prod_mod)
pp_check(browser_prod_mod) #no better


hypothesis(browser_prod_mod, "turf_productivity_c>0") #0.68-->0.66


##brusher---
brusher_prod_mod<-
  brm(productivity_kg_ha_day ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = brusher_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/brusher_prod_mod") #19 divergent trans
print(brusher_prod_mod) 
pp_check(brusher_prod_mod) #looks pretty good

hypothesis(brusher_prod_mod, "turf_productivity_c>0") #  0.71		(same)


##cropper---
cropper_prod_mod<-
  brm(productivity_kg_ha_day ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = cropper_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/cropper_prod_mod") #0 divergent trans
print(cropper_prod_mod) 
pp_check(cropper_prod_mod) #way worse*

hypothesis(cropper_prod_mod, "turf_productivity_c>0") #0.78	 --> 0.8


##excavator---
excavator_prod_mod<-
  brm(productivity_kg_ha_day ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = excavator_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/excavator_prod_mod") #14 divergent trans
print(excavator_prod_mod)
pp_check(excavator_prod_mod) #looks good

hypothesis(excavator_prod_mod, "turf_productivity_c>0")  #     0.2	 --> 0.2


##farmer---
farmer_prod_mod<-
  brm(productivity_kg_ha_day ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = farmer_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/farmer_prod_mod") #11 divergent trans
print(farmer_prod_mod) 
pp_check(farmer_prod_mod) #looks good


hypothesis(farmer_prod_mod, "turf_productivity_c>0") #    	0.22	-->     	0.23


##scraper---
scraper_prod_mod<-
  brm(productivity_kg_ha_day ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = scraper_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/scraper_prod_mod") #2 divergent trans
print(scraper_prod_mod) 
pp_check(scraper_prod_mod) #looks good

hypothesis(scraper_prod_mod, "turf_productivity_c>0") #0.63 --> 0.64

#all conclusions identical, proceed with log because contrasins above 0 (makes more sense), and some better sampling.

```



####Bayesian analysis based on DAGs - effect of turf productivity on herbivore biomass, by feeding group----
```{r}

##browser---
browser_bio_log_mod<-
  brm(log_herb_bio ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = browser_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/browser_bio_log_mod") #1 divergent trans
print(browser_bio_log_mod)
pp_check(browser_bio_log_mod) #a bit hump-shaped, not terrible


hypothesis(browser_bio_log_mod, "turf_productivity_c>0")
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	   14.79	    20.31	    -17.3	    45.65           	4.52            	0.82	



##brusher---
brusher_bio_log_mod<-
  brm(log_herb_bio ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = brusher_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/brusher_bio_log_mod") #0 divergent trans
print(brusher_bio_log_mod) 
plot(brusher_bio_log_mod)
pp_check(brusher_bio_log_mod) #looks pretty good


hypothesis(brusher_bio_log_mod, "turf_productivity_c>0") 
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	    6.73    	20.67	    -20.91      	39.61	      2.01                	0.67		




##cropper---
cropper_bio_log_mod<-
  brm(log_herb_bio ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = cropper_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/cropper_bio_log_mod") #0 divergent trans
print(cropper_bio_log_mod) 
plot(cropper_bio_log_mod)
pp_check(cropper_bio_log_mod) #not quite sampling peak, but not bad


hypothesis(cropper_bio_log_mod, "turf_productivity_c>0") 
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	      13.56	    16.35	  -9.85	    37.14	          6.68                	0.87	



##excavator---
excavator_bio_log_mod<-
  brm(log_herb_bio ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = excavator_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/excavator_bio_log_mod") #0 divergent trans
print(excavator_bio_log_mod)
plot(excavator_bio_log_mod)
pp_check(excavator_bio_log_mod) #a bit hump-shaped, but pretty good


hypothesis(excavator_bio_log_mod, "turf_productivity_c>0") 
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	     -16.39	    22.71	    -54.51	  16.36	        0.23                	0.19	
1 



##farmer---
farmer_bio_log_mod<-
  brm(log_herb_bio ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = farmer_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/farmer_bio_log_mod") #0 divergent trans
print(farmer_bio_log_mod) 
plot(farmer_bio_log_mod)
pp_check(farmer_bio_log_mod) #a bit hump-shaped, but pretty good


hypothesis(farmer_bio_log_mod, "turf_productivity_c>0") 
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	   -18.73	        37.03	  -65.96  	20.52       	0.21              	0.18	



##scraper---
scraper_bio_log_mod<-
  brm(log_herb_bio ~ turf_productivity_c + turf_n15_c  + (1|Island), 
       data = scraper_dat_c,
        iter = 3000, warmup = 1000, chains = 4, cores = 4,
         control = list(adapt_delta = 0.999, max_treedepth = 15), 
       file = "../outputs/brms/scraper_bio_log_mod") # 0 divergent trans
print(scraper_bio_log_mod) 
plot(scraper_bio_log_mod)
pp_check(scraper_bio_log_mod) #looks good


hypothesis(scraper_bio_log_mod, "turf_productivity_c>0") 
#hypothesis                     est      error     lower     upper       evidence ratio        posterior probability
#(turf_productivit... > 0	    	9.37    	23.32	    -26.96	  44.52	      2.49	                      0.71	



```

#extract effect sizes and 95% hpdis:
```{r}


#productivity models:-----
cropper_prod_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#0.1216613	-0.6723181	0.9059609	


cropper_prod_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(exp(b_turf_productivity_c/10)) 
#back-transform: 
#1.129372	0.2993779	1.935624	
#for each 0.1 mm/day increase in turf growth, cropper productivity increases by a factor of 1.13 (95% HPDI 0.30 to 1.94).

brusher_prod_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#0.01359768	-0.1720333	0.2097179	


scraper_prod_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#0.03682815	-0.529185	0.7166251	


excavator_prod_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#-0.05871047	-0.6127007	0.3318234	

farmer_prod_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#-0.02058008	-0.1979979	0.1246575	


browser_prod_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#0.03488947	-0.3704969	0.6525071	

#biomass models:-----
cropper_bio_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#1.351464	-1.727903	4.398507	

cropper_bio_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(exp(b_turf_productivity_c/10)) 
#back-transform: 
#3.863077	1.730786e-07	41.04903
#for each 0.1 mm/day increase in turf growth, cropper productivity increases by a factor of 3.86 (95% HPDI 0 to 41.0).


brusher_bio_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#0.5470305	-3.217795	5.033131	


scraper_bio_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#0.950204	-3.709407	5.600817	


excavator_bio_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#-1.448938	-6.429473	2.830282	

farmer_bio_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#-1.740312	-8.108458	3.699947	0.95	median	hdi


browser_bio_log_mod %>%
  spread_draws(b_turf_productivity_c) %>% 
  median_hdci(b_turf_productivity_c/10) #make scale reasonable - 0.1 mm increase in turf growth/day, rather than 1 mm increase
#1.491909	-2.679731	5.585599	


```



##plot prediction lines:
```{r}

#productivity------
#combine data and plot in different facets:
me_farmer<-conditional_effects(farmer_prod_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_farmer<-partialize(farmer_prod_log_mod, vars= "turf_productivity_c",  data = farmer_dat_c)

me_scraper<-conditional_effects(scraper_prod_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_scraper<-partialize(scraper_prod_log_mod, vars= "turf_productivity_c",  data = scraper_dat_c)

me_excavator<-conditional_effects(excavator_prod_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_excavator<-partialize(excavator_prod_log_mod, vars= "turf_productivity_c",  data = excavator_dat_c)

me_brusher<-conditional_effects(brusher_prod_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_brusher<-partialize(brusher_prod_log_mod, vars= "turf_productivity_c",  data = brusher_dat_c)

me_cropper<-conditional_effects(cropper_prod_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_cropper<-partialize(cropper_prod_log_mod, vars= "turf_productivity_c",  data = cropper_dat_c)

me_browser<-conditional_effects(browser_prod_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_browser<-partialize(browser_prod_log_mod, vars= "turf_productivity_c",  data = browser_dat_c)



comb_me<-bind_rows(list(me_cropper, me_brusher, me_scraper, me_excavator, me_farmer,   me_browser), .id = "id")%>%
  mutate(fg.fine = case_when(id == 1 ~ "cropper",
                             id == 2 ~ "brusher",
                             id == 3 ~ "scraper",
                             id == 4 ~ "excavator",
                             id == 5 ~ "farmer",
                             id == 6 ~ "browser"))%>%
  mutate(fg.fine = as.factor(fg.fine))%>%
  mutate(fg.fine = fct_relevel(fg.fine, "cropper", "brusher", "scraper", "excavator", "farmer", "browser"))


#uncenter and scale
comb_mep_unscale<-
  comb_me%>%
  mutate(mean_turf_prod_mm_day = turf_productivity_c+ 0.3158526 )# + mean


comb_p<-bind_rows(list(p_cropper, p_brusher, p_scraper, p_excavator, p_farmer,   p_browser), .id = "id")%>%
  mutate(fg.fine = case_when(id == 1 ~ "cropper", #(turf algae)
                             id == 2 ~ "brusher",
                             id == 3 ~ "scraper",
                             id == 4 ~ "excavator",
                             id == 5 ~ "farmer",
                             id == 6 ~ "browser"))%>% #(macroalgae)
  mutate(fg.fine = as.factor(fg.fine))%>%
  mutate(fg.fine = fct_relevel(fg.fine, "cropper", "brusher", "scraper", "excavator", "farmer", "browser"))


###add better labels:
fine_fg_part_plot<-
comb_mep_unscale %>%
  ggplot(aes(x = mean_turf_prod_mm_day, y = log_herb_prod, fill = fg.fine)) +
      geom_line(aes(x = mean_turf_prod_mm_day, y = estimate__, colour = fg.fine), lwd = 1.2) +
 geom_point(data = comb_p, aes(x = mean_turf_prod_mm_day, y = log_herb_prod, colour = fg.fine)) +
        geom_ribbon(aes(ymin = lower__, ymax=upper__), alpha = .2) +
  facet_wrap(~fg.fine, strip.position = "top",
             labeller = labeller(fg.fine = c("cropper" = "(a) croppers (turf algae)", 
                                                       "brusher" = "(b) brushers (detritus)",
                                                        "scraper" = "(c) scrapers (cyanobacteria)", 
                                                        "excavator" = "(d) excavators (cyanobacteria)", 
                                                        "farmer" = "(e) farmers (turf algae in territory)", 
                                                        "browser" = "(f) browsers (macroalgae)")))+
  scale_fill_brewer(palette = "Set2")+
    scale_colour_brewer(palette = "Set2")+
  ylab(bquote(Herbivore~productivity~(log~kg~ha^-1~day^-1)))+
  xlab(bquote(Turf~productivity~(mm~day^-1)))+
  theme_bw()+
    guides(size = "none", colour = "none",  fill = guide_legend(title="Confidence level")) + 
    theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
    #            text = element_text(size = 24),
        legend.position='none',
        strip.text = element_text(hjust = 0, margin = margin(1, 0, 1, 0, "pt"), size = 8),
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8))
fine_fg_part_plot

#save-----
#ggsave(filename = "../outputs/figures/fine_fg_part_plot_prod_smaller_font.png",  plot = fine_fg_part_plot,width = 15,  height = 10,units = "cm",dpi = 300)

#ggsave(filename = "../outputs/figures/fine_fg_part_plot_prod_smaller_font.pdf",  plot = fine_fg_part_plot,width = 15,  height = 10,units = "cm",dpi = 300)


```


##plot biomass results + raw data, by FG
```{r}

#biomass------
#combine data and plot in different facets:
me_farmer<-conditional_effects(farmer_bio_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_farmer<-partialize(farmer_bio_log_mod, vars= "turf_productivity_c",  data = farmer_dat_c)

me_scraper<-conditional_effects(scraper_bio_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_scraper<-partialize(scraper_bio_log_mod, vars= "turf_productivity_c",  data = scraper_dat_c)

me_excavator<-conditional_effects(excavator_bio_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_excavator<-partialize(excavator_bio_log_mod, vars= "turf_productivity_c",  data = excavator_dat_c)

me_brusher<-conditional_effects(brusher_bio_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_brusher<-partialize(brusher_bio_log_mod, vars= "turf_productivity_c",  data = brusher_dat_c)

me_cropper<-conditional_effects(cropper_bio_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_cropper<-partialize(cropper_bio_log_mod, vars= "turf_productivity_c",  data = cropper_dat_c)

me_browser<-conditional_effects(browser_bio_log_mod, prob = .75, effects = 'turf_productivity_c', plot = FALSE)[[1]]
p_browser<-partialize(browser_bio_log_mod, vars= "turf_productivity_c",  data = browser_dat_c)



comb_me<-bind_rows(list(me_cropper, me_brusher, me_scraper, me_excavator, me_farmer,   me_browser), .id = "id")%>%
  mutate(fg.fine = case_when(id == 1 ~ "cropper",
                             id == 2 ~ "brusher",
                             id == 3 ~ "scraper",
                             id == 4 ~ "excavator",
                             id == 5 ~ "farmer",
                             id == 6 ~ "browser"))%>%
  mutate(fg.fine = as.factor(fg.fine))%>%
  mutate(fg.fine = fct_relevel(fg.fine, "cropper", "brusher", "scraper", "excavator", "farmer", "browser"))


#uncenter and scale
comb_meb_unscale<-
  comb_me%>%
  mutate(mean_turf_prod_mm_day = turf_productivity_c+ 0.3158526 )# + mean


comb_b<-bind_rows(list(p_cropper, p_brusher, p_scraper, p_excavator, p_farmer,   p_browser), .id = "id")%>%
  mutate(fg.fine = case_when(id == 1 ~ "cropper", #(turf algae)
                             id == 2 ~ "brusher",
                             id == 3 ~ "scraper",
                             id == 4 ~ "excavator",
                             id == 5 ~ "farmer",
                             id == 6 ~ "browser"))%>% #(macroalgae)
  mutate(fg.fine = as.factor(fg.fine))%>%
  mutate(fg.fine = fct_relevel(fg.fine, "cropper", "brusher", "scraper", "excavator", "farmer", "browser"))


###add better labels:
fine_fg_part_plot_bio<-
comb_meb_unscale %>%
  ggplot(aes(x = mean_turf_prod_mm_day, y = log_herb_bio, fill = fg.fine)) +
      geom_line(aes(x = mean_turf_prod_mm_day, y = estimate__, colour = fg.fine), lwd = 1.2) +
 geom_point(data = comb_b, aes(x = mean_turf_prod_mm_day, y = log_herb_bio, colour = fg.fine)) +
        geom_ribbon(aes(ymin = lower__, ymax=upper__), alpha = .2) +
  facet_wrap(~fg.fine, strip.position = "top",
             labeller = labeller(fg.fine = c("cropper" = "(a) croppers (turf algae)", 
                                                       "brusher" = "(b) brushers (detritus)",
                                                        "scraper" = "(c) scrapers (cyanobacteria)", 
                                                        "excavator" = "(d) excavators (cyanobacteria)", 
                                                        "farmer" = "(e) farmers (turf algae in territory)", 
                                                        "browser" = "(f) browsers (macroalgae)")))+
  scale_fill_brewer(palette = "Set2")+
    scale_colour_brewer(palette = "Set2")+
  ylab(bquote(Herbivore~biomass~(log~kg~ha^-1)))+
  xlab(bquote(Turf~productivity~(mm~day^-1)))+
  theme_bw()+
    guides(size = "none", colour = "none",  fill = guide_legend(title="Confidence level")) + 
    theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
               text = element_text(size = 8),
        legend.position='none',
        strip.text = element_text(hjust = 0, margin = margin(1, 0, 1, 0, "pt"), size = 8),
        axis.text = element_text(size = 6),
    axis.title = element_text(size = 8))
fine_fg_part_plot_bio

#save-----
ggsave(filename = "../outputs/figures/fine_fg_part_plot_bio_smaller_font.png",  plot = fine_fg_part_plot_bio,width = 15,  height = 10,units = "cm",dpi = 300)

ggsave(filename = "../outputs/figures/fine_fg_part_plot_bio_smaller_font.pdf",  plot = fine_fg_part_plot_bio,width = 15,  height = 10,units = "cm",dpi = 300)
```