---
title: "wave calculations"
author: "CEB"
date: '2025-01-02'
output: html_document
---

#load packages
```{r}
library(tidyverse)
library(waver)
citation('waver')


options(scipen = 9999)
```

#load gps data
```{r}
isl_gps_dat<-read.csv("../data/seychelles_gps.csv", stringsAsFactors = TRUE) 
isl_gps_dat

#add rat categories:
sb_dat_used_gps<-
  isl_gps_dat%>%
  mutate(rat_status = case_when(Island == "Aride"~ "never rats",
                                Island == "Cousine"~ "never rats",
                                Island == "Felicite"~ "rats",
                                Island == "Fregate"~ "rats eradicated"))

sb_dat_used_gps


#transform data to spatial object and map:
sb_dat_used_gps_sf <- st_as_sf(sb_dat_used_gps, coords = c("Longitude", "Latitude"),  crs = 4326)


```

#load shoreline data
```{r}
#should just need seychelles, because all else is >650 km away

my_sf <- read_sf("../data/shape_files/syc_admbnda_adm0_nbs2010.shp")

```


#load wind direction and speed data - combine with fetch data
```{r}

#need to have wind speed (check), then wind direction - but this will just be used for fetch in that direction, so then we will have wind speed and fetch for each site (at each wind measurement). Fetch will change based on wind direction.

#load full wind data - from Seychelles
dir_dat<-read.csv("../data/SEYCHELLES AIRPORT_hrly_wind_dir_2012_2022.csv")
#NOTE: Data from 1st Jan 2012 to 31st December 2017 are from manned station and from 1st January 2018 to 31st Dec 2022 from AWOS 

speed_dat<-read.csv("../data/SEYCHELLES AIRPORT_hrly_wind_speed_2012_2022.csv")
#note: unit = KNOTS


#make long:
dir_dat_long<-
  dir_dat%>%
  pivot_longer(names_to = "hour", cols = c(X0:X23), values_to = "direction")
dir_dat_long

speed_dat_long<-
  speed_dat%>%
  pivot_longer(names_to = "hour", cols = c(X0:X23), values_to = "speed_knots")
speed_dat_long


#combine:
wind_dat_long<-
  full_join(dir_dat_long, speed_dat_long)%>%
  mutate(speed_ms = speed_knots/1.94384)
wind_dat_long
#perfect!


#determine how to bin/match fetch direction and wind directin:
#from Graham et al 2015:Fetch values for each of our 21 reefs was calculated in 32 compass directions (each with an angular width of 11.25) 
sey_fetch_dat_32<-fetch_len_multi(pts = sb_dat_used_gps_sf, shoreline = my_sf, bearings = c(0, 11.25, 22.5, 33.75, 45, 56.25, 67.5, 78.75,
                                                                                            90, 101.25, 112.5,123.75, 135, 146.25, 157.5, 168.75, 
                                                                                            180,191.25, 202.5,213.75,  225, 236.25, 247.5, 258.75, 
                                                                                            270, 281.25, 292.5, 303.75, 315, 326.25, 337.5, 348.75), dmax = 650000)
sey_fetch_dat_32

#write to csv because takes time to calculate:
#write.csv(sey_fetch_dat_32, "../data/sey_fetch_dat_32.csv")


#add site names in there, and reload:
fetch_dat<-read.csv("../data/sey_fetch_dat_32_wsite.csv")
fetch_dat


#now, for each wind direction, match it with the closest fetch direction:
#so we did 11.25 for angular width, which means for each point, the closest wind directions are between point-5.625, and point + 5.625
wind_dat_long%>%
  distinct(direction)

wind_dat_long_fetch<-
  wind_dat_long%>%
  mutate(fetch_direction = case_when((direction>354.375|direction<=5.625)~0,
                                     (direction>5.625&direction<=16.875)~11.25,
                                     (direction>16.875&direction<=28.125)~22.5,
                                     (direction>28.125&direction<=39.375)~33.75,
                                     (direction>39.375&direction<=50.625)~45,
                                     (direction>50.625&direction<=61.875)~56.25,
                                     (direction>61.875&direction<=73.125)~67.5,
                                     (direction>73.125&direction<=84.375)~78.75,
                                     (direction>84.375&direction<=95.625)~90,
                                     (direction>95.625&direction<=106.875)~101.25,
                                     (direction>106.875&direction<=118.125)~112.5,
                                     (direction>118.125&direction<=129.375)~123.75,
                                     (direction>129.375&direction<=140.625)~135,
                                     (direction>140.625&direction<=151.875)~146.25,
                                     (direction>151.875&direction<=163.125)~157.5,
                                     (direction>163.125&direction<=174.375)~168.75,
                                     (direction>174.375&direction<=185.625)~180,
                                     (direction>185.625&direction<=196.875)~191.25,
                                     (direction>196.875&direction<=208.125)~202.5,
                                     (direction>208.125&direction<=219.375)~213.75,
                                     (direction>219.375&direction<=230.625)~225,
                                     (direction>230.625&direction<=241.875)~236.25,
                                     (direction>241.875&direction<=253.125)~247.5,
                                     (direction>253.125&direction<=264.375)~258.75,
                                       (direction>264.375&direction<=275.625)~270,
                                       (direction>275.625&direction<=286.875)~281.25,
                                       (direction>286.875&direction<=298.125)~292.5,
                                       (direction>298.125&direction<=309.375)~303.75,
                                       (direction>309.375&direction<=320.625)~315,
                                       (direction>320.625&direction<=331.875)~326.25,
                                       (direction>331.875&direction<=343.125)~337.5,
                                       (direction>343.125&direction<=354.375)~348.75))
                                
 wind_dat_long_fetch    
#not the most efficient way, but clearly worked!

```


#okay, now for each location, need to calculate wave height for each hourly interval, based on wind speed and fetch in that direction
```{r}
#change fetch data to long, so we can just add columns for each site to the wind_fetch data above, merging based on direction:
fetch_dat

fetch_dat_long<-
  fetch_dat%>%
  pivot_longer(values_to = "fetch_length", names_to = "fetch_direction", cols = c(X0:X348.75))%>%
  mutate(fetch_direction = gsub("X", "", fetch_direction))%>%
  mutate(fetch_direction = as.numeric(fetch_direction))
fetch_dat_long
#actually, not quite what I want. need fetch_length_site for each fetch_direction

fetch_dat_wide<-
  fetch_dat_long%>%
  pivot_wider(names_from = c(Island_Site), values_from = fetch_length, names_prefix = "fetch_length_")
fetch_dat_wide



wind_dat_long_fetch



#now merge:
wind_and_fetch_dat<-
  left_join(wind_dat_long_fetch, fetch_dat_wide, by = join_by(fetch_direction))
wind_and_fetch_dat
#perfect!

```


#now calculate wave height and wave energy for each wind speed and direction plus fetch length for each island: MANUAL BASED ON REFERENCES
#FIRST FOR ARIDE
```{r}
##do one site at a time, and remove NAs:
wind_and_fetch_dat_manual_noNA<-
  wind_and_fetch_dat%>%
  filter(!(is.na(speed_ms)))%>%
  filter(!(is.na(fetch_direction)))
wind_and_fetch_dat_manual_noNA


wind_and_fetch_dat_manual_Aride<-
  wind_and_fetch_dat_manual_noNA%>%
  select(!c(fetch_length_Cousine_1, fetch_length_Felicite_1, fetch_length_Fregate_H, fetch_length_Fregate_L)) #fetch_length_Aride_1
wind_and_fetch_dat_manual_Aride



#first check if each reading is fetch-limited:----
#1.	A pixel is classed as fetch limited for this direction if the non-dimensional fetch ξ (Resio et al. 2003) is less than a threshold value of 38,590 m:
#(9.81*fetch_m)/(wind_speed_ms^2)
#is that < 38590??
wind_and_fetch_dat_manual_Aride1<-
   wind_and_fetch_dat_manual_Aride%>%
   rowwise()%>%
  mutate(non_dim_fetch_Aride = (9.81*fetch_length_Aride_1)/(speed_ms^2))%>%
  mutate(fetch_limited_Aride = case_when(non_dim_fetch_Aride<38590 ~"No",
                                         TRUE~"Yes"))
#note: getting "Inf" when wind speed = 0, but this will end up as 0 no matter what so doesn't matter....
wind_and_fetch_dat_manual_Aride1

##add wave height column-----
#not fetch-limited:
#wave height = 0.00082*(windspeed_m_s)^1.1*(fetch_m)^0.45

#fetch-limited:
#wave height = 0.034*(windspeed_m_s)^2

wind_and_fetch_dat_manual_Aride2<-
  wind_and_fetch_dat_manual_Aride1%>%
  rowwise()%>%
  mutate(wave_height_Aride = case_when(fetch_limited_Aride=="No"~
                                         (0.00082*(speed_ms)^1.1*(fetch_length_Aride_1)^0.45),
                                       fetch_limited_Aride=="Yes"~ (0.034*(speed_ms)^2)))

wind_and_fetch_dat_manual_Aride2


#add wave energy column----
#wave energy = (1/16)*1030*9.81*wave_height^2 


wind_and_fetch_dat_manual_Aride3<-
  wind_and_fetch_dat_manual_Aride2%>%
  rowwise()%>%
  mutate(wave_energy_Aride = (1/16)*1030*9.81*wave_height_Aride^2)
  
wind_and_fetch_dat_manual_Aride3


#now get long-term average, which is calculated as the geometric mean of the individual energy estimates:

#limit to 10 years prior to data collection, so November 2012-November 2022:
wind_and_fetch_dat_manual_Aride_10_year<-
  wind_and_fetch_dat_manual_Aride3%>%
  filter(!(yyyy == 2012 & mm <=10))%>%
  filter(!(yyyy == 2022 & mm > 11))
wind_and_fetch_dat_manual_Aride_10_year

mean(wind_and_fetch_dat_manual_Aride_10_year$wave_energy_Aride)


```

##REPEAT FOR OTHER SITES:
#COUSINE
```{r}

wind_and_fetch_dat_manual_Cousine<-
  wind_and_fetch_dat_manual_noNA%>%
  select(!c(fetch_length_Aride_1, fetch_length_Felicite_1, fetch_length_Fregate_H, fetch_length_Fregate_L)) #fetch_length_Cousine_1
wind_and_fetch_dat_manual_Cousine



#first check if each reading is fetch-limited:----
#1.	A pixel is classed as fetch limited for this direction if the non-dimensional fetch ξ (Resio et al. 2003) is less than a threshold value of 38,590 m:
#(9.81*fetch_m)/(wind_speed_ms^2)
#is that < 38590??
wind_and_fetch_dat_manual_Cousine1<-
   wind_and_fetch_dat_manual_Cousine%>%
   rowwise()%>%
  mutate(non_dim_fetch_Cousine = (9.81*fetch_length_Cousine_1)/(speed_ms^2))%>%
  mutate(fetch_limited_Cousine = case_when(non_dim_fetch_Cousine<38590 ~"No",
                                         TRUE~"Yes"))
#note: getting "Inf" when wind speed = 0, but this will end up as 0 no matter what so doesn't matter....
wind_and_fetch_dat_manual_Cousine1

##add wave height column-----
#not fetch-limited:
#wave height = 0.00082*(windspeed_m_s)^1.1*(fetch_m)^0.45

#fetch-limited:
#wave height = 0.034*(windspeed_m_s)^2

wind_and_fetch_dat_manual_Cousine2<-
  wind_and_fetch_dat_manual_Cousine1%>%
  rowwise()%>%
  mutate(wave_height_Cousine = case_when(fetch_limited_Cousine=="No"~
                                         (0.00082*(speed_ms)^1.1*(fetch_length_Cousine_1)^0.45),
                                       fetch_limited_Cousine=="Yes"~ (0.034*(speed_ms)^2)))

wind_and_fetch_dat_manual_Cousine2


#add wave energy column----
#wave energy = (1/16)*1030*9.81*wave_height^2 


wind_and_fetch_dat_manual_Cousine3<-
  wind_and_fetch_dat_manual_Cousine2%>%
  rowwise()%>%
  mutate(wave_energy_Cousine = (1/16)*1030*9.81*wave_height_Cousine^2)
  
wind_and_fetch_dat_manual_Cousine3


#now get long-term average, which is calculated as the geometric mean of the individual energy estimates:

#limit to 10 years prior to data collection, so November 2012-November 2022:
wind_and_fetch_dat_manual_Cousine_10_year<-
  wind_and_fetch_dat_manual_Cousine3%>%
  filter(!(yyyy == 2012 & mm <=10))%>%
  filter(!(yyyy == 2022 & mm > 11))
wind_and_fetch_dat_manual_Cousine_10_year

mean(wind_and_fetch_dat_manual_Cousine_10_year$wave_energy_Cousine)


```

#FELICITE
```{r}

wind_and_fetch_dat_manual_Felicite<-
  wind_and_fetch_dat_manual_noNA%>%
  select(!c(fetch_length_Aride_1, fetch_length_Cousine_1, fetch_length_Fregate_H, fetch_length_Fregate_L)) #fetch_length_Felicite_1
wind_and_fetch_dat_manual_Felicite



#first check if each reading is fetch-limited:----
#1.	A pixel is classed as fetch limited for this direction if the non-dimensional fetch ξ (Resio et al. 2003) is less than a threshold value of 38,590 m:
#(9.81*fetch_m)/(wind_speed_ms^2)
#is that < 38590??
wind_and_fetch_dat_manual_Felicite1<-
   wind_and_fetch_dat_manual_Felicite%>%
   rowwise()%>%
  mutate(non_dim_fetch_Felicite = (9.81*fetch_length_Felicite_1)/(speed_ms^2))%>%
  mutate(fetch_limited_Felicite = case_when(non_dim_fetch_Felicite<38590 ~"No",
                                         TRUE~"Yes"))
#note: getting "Inf" when wind speed = 0, but this will end up as 0 no matter what so doesn't matter....
wind_and_fetch_dat_manual_Felicite1

##add wave height column-----
#not fetch-limited:
#wave height = 0.00082*(windspeed_m_s)^1.1*(fetch_m)^0.45

#fetch-limited:
#wave height = 0.034*(windspeed_m_s)^2

wind_and_fetch_dat_manual_Felicite2<-
  wind_and_fetch_dat_manual_Felicite1%>%
  rowwise()%>%
  mutate(wave_height_Felicite = case_when(fetch_limited_Felicite=="No"~
                                         (0.00082*(speed_ms)^1.1*(fetch_length_Felicite_1)^0.45),
                                       fetch_limited_Felicite=="Yes"~ (0.034*(speed_ms)^2)))

wind_and_fetch_dat_manual_Felicite2


#add wave energy column----
#wave energy = (1/16)*1030*9.81*wave_height^2 


wind_and_fetch_dat_manual_Felicite3<-
  wind_and_fetch_dat_manual_Felicite2%>%
  rowwise()%>%
  mutate(wave_energy_Felicite = (1/16)*1030*9.81*wave_height_Felicite^2)
  
wind_and_fetch_dat_manual_Felicite3


#now get long-term average, which is calculated as the geometric mean of the individual energy estimates:

#limit to 10 years prior to data collection, so November 2012-November 2022:
wind_and_fetch_dat_manual_Felicite_10_year<-
  wind_and_fetch_dat_manual_Felicite3%>%
  filter(!(yyyy == 2012 & mm <=10))%>%
  filter(!(yyyy == 2022 & mm > 11))
wind_and_fetch_dat_manual_Felicite_10_year

mean(wind_and_fetch_dat_manual_Felicite_10_year$wave_energy_Felicite)


```




#FREGATE H
```{r}

wind_and_fetch_dat_manual_Fregate_H<-
  wind_and_fetch_dat_manual_noNA%>%
  select(!c(fetch_length_Aride_1, fetch_length_Cousine_1, fetch_length_Felicite_1, fetch_length_Fregate_L)) #fetch_length_Felicite_1
wind_and_fetch_dat_manual_Fregate_H



#first check if each reading is fetch-limited:----
#1.	A pixel is classed as fetch limited for this direction if the non-dimensional fetch ξ (Resio et al. 2003) is less than a threshold value of 38,590 m:
#(9.81*fetch_m)/(wind_speed_ms^2)
#is that < 38590??
wind_and_fetch_dat_manual_Fregate_H1<-
   wind_and_fetch_dat_manual_Fregate_H%>%
   rowwise()%>%
  mutate(non_dim_fetch_Fregate_H = (9.81*fetch_length_Fregate_H)/(speed_ms^2))%>%
  mutate(fetch_limited_Fregate_H = case_when(non_dim_fetch_Fregate_H<38590 ~"No",
                                         TRUE~"Yes"))
#note: getting "Inf" when wind speed = 0, but this will end up as 0 no matter what so doesn't matter....
wind_and_fetch_dat_manual_Fregate_H1

##add wave height column-----
#not fetch-limited:
#wave height = 0.00082*(windspeed_m_s)^1.1*(fetch_m)^0.45

#fetch-limited:
#wave height = 0.034*(windspeed_m_s)^2

wind_and_fetch_dat_manual_Fregate_H2<-
  wind_and_fetch_dat_manual_Fregate_H1%>%
  rowwise()%>%
  mutate(wave_height_Fregate_H = case_when(fetch_limited_Fregate_H=="No"~
                                         (0.00082*(speed_ms)^1.1*(fetch_length_Fregate_H)^0.45),
                                       fetch_limited_Fregate_H=="Yes"~ (0.034*(speed_ms)^2)))

wind_and_fetch_dat_manual_Fregate_H2


#add wave energy column----
#wave energy = (1/16)*1030*9.81*wave_height^2 


wind_and_fetch_dat_manual_Fregate_H3<-
  wind_and_fetch_dat_manual_Fregate_H2%>%
  rowwise()%>%
  mutate(wave_energy_Fregate_H = (1/16)*1030*9.81*wave_height_Fregate_H^2)
  
wind_and_fetch_dat_manual_Fregate_H3


#now get long-term average, which is calculated as the geometric mean of the individual energy estimates:

#limit to 10 years prior to data collection, so November 2012-November 2022:
wind_and_fetch_dat_manual_Fregate_H_10_year<-
  wind_and_fetch_dat_manual_Fregate_H3%>%
  filter(!(yyyy == 2012 & mm <=10))%>%
  filter(!(yyyy == 2022 & mm > 11))
wind_and_fetch_dat_manual_Fregate_H_10_year

mean(wind_and_fetch_dat_manual_Fregate_H_10_year$wave_energy_Fregate_H) 


```







#FREGATE L
```{r}

wind_and_fetch_dat_manual_Fregate_L<-
  wind_and_fetch_dat_manual_noNA%>%
  select(!c(fetch_length_Aride_1, fetch_length_Cousine_1, fetch_length_Felicite_1, fetch_length_Fregate_H)) #fetch_length_Felicite_1
wind_and_fetch_dat_manual_Fregate_L



#first check if each reading is fetch-limited:----
#1.	A pixel is classed as fetch limited for this direction if the non-dimensional fetch ξ (Resio et al. 2003) is less than a threshold value of 38,590 m:
#(9.81*fetch_m)/(wind_speed_ms^2)
#is that < 38590??
wind_and_fetch_dat_manual_Fregate_L1<-
   wind_and_fetch_dat_manual_Fregate_L%>%
   rowwise()%>%
  mutate(non_dim_fetch_Fregate_L = (9.81*fetch_length_Fregate_L)/(speed_ms^2))%>%
  mutate(fetch_limited_Fregate_L = case_when(non_dim_fetch_Fregate_L<38590 ~"No",
                                         TRUE~"Yes"))
#note: getting "Inf" when wind speed = 0, but this will end up as 0 no matter what so doesn't matter....
wind_and_fetch_dat_manual_Fregate_L1

##add wave height column-----
#not fetch-limited:
#wave height = 0.00082*(windspeed_m_s)^1.1*(fetch_m)^0.45

#fetch-limited:
#wave height = 0.034*(windspeed_m_s)^2

wind_and_fetch_dat_manual_Fregate_L2<-
  wind_and_fetch_dat_manual_Fregate_L1%>%
  rowwise()%>%
  mutate(wave_height_Fregate_L = case_when(fetch_limited_Fregate_L=="No"~
                                         (0.00082*(speed_ms)^1.1*(fetch_length_Fregate_L)^0.45),
                                       fetch_limited_Fregate_L=="Yes"~ (0.034*(speed_ms)^2)))

wind_and_fetch_dat_manual_Fregate_L2


#add wave energy column----
#wave energy = (1/16)*1030*9.81*wave_height^2 


wind_and_fetch_dat_manual_Fregate_L3<-
  wind_and_fetch_dat_manual_Fregate_L2%>%
  rowwise()%>%
  mutate(wave_energy_Fregate_L = (1/16)*1030*9.81*wave_height_Fregate_L^2)
  
wind_and_fetch_dat_manual_Fregate_L3


#now get long-term average, which is calculated as the geometric mean of the individual energy estimates:

#limit to 10 years prior to data collection, so November 2012-November 2022:
wind_and_fetch_dat_manual_Fregate_L_10_year<-
  wind_and_fetch_dat_manual_Fregate_L3%>%
  filter(!(yyyy == 2012 & mm <=10))%>%
  filter(!(yyyy == 2022 & mm > 11))
wind_and_fetch_dat_manual_Fregate_L_10_year

mean(wind_and_fetch_dat_manual_Fregate_L_10_year$wave_energy_Fregate_L)

```



##calculate 10-year average
```{r}

#merge data back together:
all_wind_fetch_manual_data<-
  left_join(wind_and_fetch_dat_manual_Fregate_H3, wind_and_fetch_dat_manual_Fregate_L3)%>%
  left_join(wind_and_fetch_dat_manual_Felicite3)%>%
    left_join(wind_and_fetch_dat_manual_Cousine3)%>%
  left_join(wind_and_fetch_dat_manual_Aride3)

#10-year average
all_wind_fetch_manual_data_10year<-
  all_wind_fetch_manual_data%>%
 filter(!(yyyy == 2012 & mm <=10))%>%
  filter(!(yyyy == 2022 & mm > 11))

mean(all_wind_fetch_manual_data_10year$wave_energy_Aride) #140.1754
mean(all_wind_fetch_manual_data_10year$wave_energy_Fregate_L) #469.6102
mean(all_wind_fetch_manual_data_10year$wave_energy_Fregate_H) #378.8382
mean(all_wind_fetch_manual_data_10year$wave_energy_Felicite) #168.3294
mean(all_wind_fetch_manual_data_10year$wave_energy_Cousine) #483.2262


```
